\documentclass{beamer}

\title{Sufficient Statistics for Welfare Analysis: A Bridge Between Structural and Reduced-Form Methods}
\author{Raj Chetty}
\date{\today}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{Introduction}
\begin{itemize}
    \item Discusses the gap between structural and reduced-form methods.
    \item Introduces sufficient-statistic approach for welfare analysis.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Key Concepts}
\begin{itemize}
    \item Sufficient Statistics: Definition and significance.
    \item Comparison with traditional approaches.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Methodology}
\begin{itemize}
    \item Framework of the sufficient-statistic approach.
    \item Key formulas and models.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Applications}
\begin{itemize}
    \item Application in income taxation.
    \item Application in social insurance.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Behavioral Models}
\begin{itemize}
    \item Application to behavioral economics.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Broader Implications}
\begin{itemize}
    \item Potential applications in various economic fields.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Conclusion}
\begin{itemize}
    \item Main findings and contributions.
    \item Importance in policy analysis.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{References}
% Add your references here
\end{frame}

\end{document}
